---
title: "pets"
author: "Rasmus Fisker Bang"
date: "25/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(drlib)
library(tidytext)

pets <- read_csv("seattle_pets.csv")

```

## Pet names in Seattle

First a look at the data

```{r}
pets
```

There are 52,519 different pets, and there 7 different variables. 
First of all I notice that `license_issue_date` needs to be a proper date variable

```{r}
pets <- pets %>% mutate(license_issue_date = mdy(license_issue_date))
```

Easy fix! Then I wonder whether `license_number` is unique?

```{r}
pets %>% count(license_number, sort = TRUE)
```

It is not, there a few pets that appear more than once, 
or some license numbers that appear again. Nevermind.

Now we can ask some questions:

### What are the most popular pet names?

```{r}
pets %>% count(animals_name, sort = TRUE) %>% 
  head(20) %>% 
  mutate(animals_name = fct_reorder(animals_name, n)) %>% 
    ggplot(aes(animals_name, n)) +
    geom_col() +
    coord_flip()
```

Apparently Lucy is very popular, and charlie. It also seems like there are a lot
pots who do not have any names?!

### How many different species of pets are there?

```{r}
pets %>% count(species, sort = TRUE)
```

Mostly cats and dogs, and some goats and a few pigs, but lets ignore does 
and remove animals without names as well

```{r}
pets <- pets %>% drop_na(animals_name) %>% 
  filter(!species %in% c("Goat","Pig"))
```

### What are the most popular cat and dog names, respectively?

```{r}
pets %>% count(species, animals_name, sort = TRUE) %>% 
  group_by(species) %>% 
  top_n(20, n) %>% 
  ungroup() %>% 
  mutate(animals_name = reorder_within(animals_name, n, species)) %>% 
  ggplot(aes(animals_name, n)) + geom_col() +
  coord_flip() +
  facet_wrap(~species, scales = "free") +
  scale_x_reordered()
```

### Which names are most specific to dogs and cats?

```{r}
pets %>% count(species, animals_name, sort = TRUE) %>% 
  spread(species, n) %>% 
  mutate(Cat = coalesce(Cat, as.integer(0)),
         Dog = coalesce(Dog, as.integer(0))) %>% 
  filter(Cat > 10, Dog > 10) %>% 
  mutate(species_measure = (Cat-Dog)/(Cat+Dog)) %>% 
  mutate(primary_species = ifelse(Cat >= Dog, "Cat", "Dog")) %>% 
  group_by(primary_species) %>% 
  top_n(10, abs(species_measure)) %>% ungroup() %>% 
  mutate(animals_name = fct_reorder(animals_name, species_measure)) %>% 
  ggplot(aes(animals_name, species_measure)) + geom_col() +
  coord_flip()
  
```















